\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity in Human Brains}

### 2014-01-14 docs/paper/paper final.tex
Added section on unfaithfulness check.

Also, the condition on line \ref{alg:pc_alg:v_struct} to orient $X - Y - Z$ according to the V-structure-rule has been made more strict.
As multiple separating sets have been found instead of only one, it needs to be checked whether $Y$ is in not in \emph{any} of those sets before the V-structure can be oriented.
In addition to the original condition, $X$ and $Z$ are tested for \textit{d}-separation given $\{Y\}$.
If they are found to be conditionally dependent, the triple is oriented as as $X \srightarrow Y \sleftarrow Z$.
%As a final safe-guard, all unshielded triples are checked for unfaithfulness and marked as such if applicable using found separating sets. %TODO wat bedoel je hiermee?
%TODO Willen we nog iets over unfaithful dingen zeggen? Zo ja, dan wel een antwoord op deze vragen...
% TODO: How do you mark unfaithful triples? can you spot the impact in the output?

>>>>

Also, the condition on line \ref{alg:pc_alg:v_struct} to orient $X - Y - Z$ according to the V-structure-rule has been made more strict.
As multiple separating sets have been found instead of only one, it needs to be checked whether $Y$ is in not in \emph{any} of those sets before the V-structure can be oriented.
In addition to this original condition, $X$ and $Z$ are \textit{explicitly} tested for \textit{d}-separation given $\{Y\}$.
If they are found to be conditionally \textit{dependent}, the triple is oriented as as $X \srightarrow Y \sleftarrow Z$.
Otherwise it is not oriented.

Given the found separating sets, it is possible to test whether these sets provide a consistent answer to the question whether the unshielded triple $\left<X,Y,Z\right>$ is \textit{d}-separated by $Y$.
It should be the case that $Y$ occurs in all found separating sets.
If this is not the case, the triple is marked as unfaithful.
This can be used as a diagnostic to judge initial reliability of results without almost any additional computational cost.
The marked triples could be coloured differently in the resulting 
The downside of this additional check is results are merely used as a diagnostic and thus the unshielded triple is oriented in a v-structure nevertheless.
It is also not a complete check as this would require as many tests as in CPC and thus no positive conclusions can be drawn from it.
Also if an unfaithful triple is detected, the impact on the final output is unclear as errors might have cascaded into further orientation steps.
